\documentclass[letterpaper,11pt]{article}
\usepackage{array}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{pdfpages}
\usepackage{changepage}
\usepackage{color}
\usepackage[hyphens,spaces,obeyspaces]{url}
\usepackage[colorlinks=true,urlcolor=blue,citecolor=black]{hyperref}
\usepackage[title]{appendix}

\title{\LARGE BAND\\
    \Large Unleashing Tokenized Economy}
\author{
        Soravis Srinawakoon\\
        \small\href{mailto:soravis@bandprotocol.com}
            {\nolinkurl{soravis@bandprotocol.com}}
    \and
        Sorawit Suriyakarn\\
        \small\href{mailto:swit@bandprotocol.com}
            {\nolinkurl{swit@bandprotocol.com}}
    }
\date{\today\\\small Draft Version 0.1.0}
\begin{document}

\maketitle

\begin{abstract}

Band Protocol is a decentralized, permissionless blockchain protocol to create tokenized marketplace and token-curated community. Band Protocol enables seamless issuance of personalized Community Token through a continuous bonding curve, a smart contract that mints and burned personalized token through a predefined mathematical function based on current circulating supply. Any entities ranging from businesses, brands and celebrities can create a loyal token-curated community with personalized tokens. Personalized Community Token is a utility token representing primary currency, subscription, discount, reward point, or any other use cases within the community as defined by the Community Manager.

Band Protocol standardizes Product Token as a way for community manager to issue products and services. It enables both tokenized real-world products as well as new digital asset creation such as rare digital collectibles and attention token.

Band Protocol enables the creation of subscription business model. Followers can stake their Community Token to a staking contract and receive regular benefits similar to normal subscription or membership. Band Protocol allows Community Manager to define their subscription tier and discount token. Discount token is a tokenized discount voucher used to reward loyal followers and incentivize active participants rather than speculators. The amount of discounts can be customized by Community Manager and in general is proportionate to the amount of total network value. Discount tokens will be an incentive for loyal followers to stake their tokens and promote the growth of the community.

Band Token is the native utility token on the delegated-proof-of-stake Band Chain. Band Token are used to secure the network, provide global liquidity to every Community Token, and act as a governance token for future protocol upgrade.

\end{abstract}

\newpage
{
\hypersetup{linkcolor=black}
\tableofcontents
}
\newpage

\section{Introduction}

\subsection{Tokenized Economy}

A typical market-based economy involves the exchange of goods and services through barter or a medium of exchange. Traditionally, buyers exchange physical coins and banknote with physical products or services offered by sellers. As technology progresses, Internet has enabled digital economy whereby goods and services are being exchanged with digital money. E-commerce experiences exponential growth as people can conveniently conduct transaction with people across the world. Centralized companies start to dominate marketplace platform and payment gateway which are key enablers of the digital economy.

Blockchain and crypto assets are giving rise to yet another revolution in the economy. Bitcoin~\cite{nakamoto}, the first cryptocurrency, becomes the first decentralized currency which enables trustless, censorship-resistant payment. Cryptocurrency such as Bitcoin allows anyone to send transaction to anyone around the world at a fraction of a cost and a fraction of time required for traditional financial institutions to conduct similar transaction. As payment and currency are being tokenized, traditional asset is slower to experience similar tokenization process. Regulation and usability are two key factors that hinder the explosive growth of asset tokenization. Asset tokenization has clear benefits:
\begin{itemize}
\item Global accessibility
\item Liquidity premium
\item Low transaction fee
\item Transparency
\item Security
\end{itemize}

Similar to how physical trade transitions to digital trade by the advancement of the Internet, the next era of commerce is the transition from centralized digital trade to decentralized token trade. Tokenized economy will become prevalent as both real-world assets and payment are being tokenized. Band Protocol enables asset tokenization and creates a standard platform for tokenized economy.
\newpage

\subsection{Use Cases}

\section{Blockchain Layer}

\subsection{Delegated Proof-of-Stake Protocol}

\subsubsection{Tendermint}

\subsubsection{Blockchain Parameters}

\subsection{Incentives and Fees}

\subsection{Cryptographic Keys}

\subsection{BAND Protocol State}

\subsubsection{Unspent Transaction Outputs (UTXOs)}

\subsubsection{Static Contracts}

\subsection{On-Chain Price Oracle}

\subsection{BAND Token}

\subsubsection{Staking}

\subsubsection{Bonding}

\subsubsection{Governance and Token-Curated Registries}

\section{BAND Protocol}

\subsection{Community Token}

\subsubsection{Value-Supply Equation}

\subsubsection{Maximum Supply}

\subsubsection{Price Spread}

\subsubsection{Purchase Flow}

\subsection{Product Token}

\subsubsection{Issuance}

\subsubsection{Redemption}

\subsubsection{Beneficiary}

\subsection{Marketplace}

\subsection{Subscription Model}

\subsubsection{Staking Contract}

\subsubsection{Discount Token}

\subsection{Attention Contracts}

\subsection{Service API Contracts}

\section{Client Layer}

\subsection{Campbase}

\subsection{Problem Definition}

\subsection{Solution}

\subsubsection{Story Feed}

\subsubsection{Fan Feed}

\subsubsection{Event}

\subsubsection{Subscription}

\subsubsection{Store}

\subsection{Community Manager}

\subsection{Consumers}

\section{Roadmap}

\bibliographystyle{unsrt}
\bibliography{paper}

\end{document}
